From Principles to Practice with Class in the First Year

### 2013-04-13 tfpie/tfpie.tex
Some work on intro.

\begin{itemize}
\item Lots of universities want their students to be proficient in an
  industrial object-oriented programming language by the end of the first year.
\item Teaching Java on Day 1 is a flawed approach.
\item Teaching functional programming in Semester 1 and Java in Semester 2 is a flawed approach.
\item We contribute a solution: a gradual transition from functional
  programming to object-oriented programming that culminates in
  industrial language proficiency.
\end{itemize}

>>>>

Many universities and colleges aim to teach their students proficiency
in an industrial object-oriented programming language by the end of
their first year.  Past approaches to achieve this aim have included
teaching an industrial language, such as Java, starting on the first
day.  Others have taken a more indirect route by teaching functional
programming in the first semester, followed by a second semester that
starts in Java.  The latter approach is an improvement over the first,
but both suffer serious flaws.

We contribute an alternative approach to the second semester that
provides a gradual transition from functional programming to
object-oriented programming that culminates in industrial language
proficiency.
